### 2023-11-02 main.tex
fixed

\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{y_{k}}}\beta_{s_{k}}^{1-c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{y_{j}}\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}c_{y_{k}}\right)
It seems to me that it is more complicated than \eqref{exactCorrelations}...

>>>>

	Equation \eqref{exactCorrelations} is obtained from \eqref{ABS_1}.\\
	Deriving correlations from \eqref{ABS}
\begin{equation}\label{exactCorrelation_1}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{1-c_{y_{k}}}\beta_{s_{k}}^{c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}(1-c_{y_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{y_{k}})\right)
In \eqref{exactCorrelations} we have the $c_{y_{k}}$ at the exponent but we remove the product over $x$.
 In \eqref{exactCorrelation_1} we have to keep the product over all $x$ and the "correlated coordinate" but we do not have the $c_{y}$ at the exponent. Which is better?
